\documentclass{exam}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{amsmath}

\let\OldTexttt\texttt

\renewcommand{\texttt}[1]{\OldTexttt{\color{teal}{#1}}}
\definecolor{mGreen}{rgb}{0,0.6,0}
\definecolor{mGray}{rgb}{0.5,0.5,0.5}
\definecolor{mPurple}{rgb}{0.58,0,0.05}
\definecolor{mGreen2}{rgb}{0.05,0.65,0.05}
\definecolor{mGray2}{rgb}{0.55,0.55,0.55}
\definecolor{mPurple2}{rgb}{0.63,0.05,0.05}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}
\definecolor{backgroundColour2}{rgb}{0.95,0.92,0.95}

\lstdefinestyle{C}{
    backgroundcolor=\color{backgroundColour},   
    commentstyle=\color{mGreen},
    keywordstyle=\color{blue},
    numberstyle=\tiny\color{mGray},
    stringstyle=\color{mPurple},    
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    language=C
}

\definecolor{t_comment}{rgb}{0.2,1,0.2}
\definecolor{t_mGray}{rgb}{0.5,0.5,0.5}
\definecolor{t_mPurple}{rgb}{0.58,0,0.05}
\definecolor{t_blue}{rgb}{0.4,0.6,0.8}
\definecolor{t_mGreen2}{rgb}{0.05,0.65,0.05}
\definecolor{t_mGray2}{rgb}{0.75,0.75,0.75}
\definecolor{t_mPurple2}{rgb}{0.63,0.05,0.05}
\definecolor{t_bg}{rgb}{0.15,0.15,0.18}

\lstdefinestyle{terminal}{
    backgroundcolor=\color{t_bg},   
    commentstyle=\color{t_comment},
    keywordstyle=\color{t_blue},
    numberstyle=\tiny\color{t_mGray},
    stringstyle=\color{t_mGray2}, 
    basicstyle=\footnotesize\color{t_mGray2},
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=none,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    language=C
}

\graphicspath{{.}}
\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
\Large{COMPSCI 3MI3 : Assignment 1} \\
\large{Fall 2021} \\ 
Instructor: Nicholas Moore \\
Maximum Grade 25/24
}}}
\end{center}

\subsection*{General Instructions}
\begin{itemize}
\item Your answers should take the form of well-reasoned arguments, proving the result the question asks for.  For every step in your solution, you should be able to say, $x$ is true, so $y$ \emph{must} be the case.  Not every step needs to be written in equations, but every step needs to be \emph{mathematical} and \emph{detailed}.  
\item Submit your answers as a PDF document.  Solutions not in PDF format will receive a 2 mark penalty.  Solutions typeset using \LaTeX will receive a 1 mark bonus, but you must also submit your source file to be eligible.  Handwritten solutions will not be accepted.   
\item The length of the text comprising a question has no correlation to the length of time required to complete it.   
\item This assignment is to be submitted through the corresponding assignment dropbox on Avenue.  
\end{itemize}

\subsection*{Questions}
\begin{questions}
\question[5] \textbf{Question 1: Reflexive Closures} \\
Suppose we are given a relation $R$ on a set $S$.  Define the relation $R'$ as follows:
$$R' = R \cup {(s,s) | s \in S}$$
That is to say, $R'$ contains all the pairs in $R$, plus all pairs of the form $(s,s)$.  Show that $R'$ is the reflexive closure of $R$.  

\question[5] \textbf{Question 2: Preservation} \\
Suppose that $R$ is a binary relation on a set $S$, and $P$ is a predicate on $S$ that preserves $R$.  Show that $P$ also preserves $P^{*}$, where $P^{*}$ is the \emph{reflexive and transitive closure} of $R$.  

\question[6] \textbf{Question 3: Transitive Closure} \\
The following is a more constructive definition of the transitive closure on a relation $R$.  First, we define the following sequence of sets of pairs.

\begin{equation}
R_0 = R 
\end{equation}
\begin{equation}
R_{i+1} = R_i \cup \{(s,u) \: | \: \text{for some} \: t, (s,t) \in R_i and (t,u) \in R_i\}
\end{equation}
Another way to say this, is that we construct each $R_i+1$ by adding to $R_i$ all the pairs that can be obtained by ``one step of transitivity'' from pairs already in $R$.  Finally, we define the relation $R^{+}$ as the union of all the $R_i$:
\begin{equation}
R^{+} = \bigcup_i R_i
\end{equation}
Show that $R^{+}$ is the transitive closure of $R$. 

\question[3] \textbf{Question 4: Ordinary Induction} \\ 
Demonstrate, using the principle of ordinary induction covered in lecuture, that each element in the Fibbonaci sequence above the $2^{nd}$ is greater than the preceeding number. 

\question[2] \textbf{Question 5: Complete Induction} \\ 
Modify the above proof to use complete induction rather than ordinary induction.

\question[3] \textbf{Question 6: Structural Induction} \\
Demonstrate, using the principle of structural induction, that, for search operations over binary search trees (\url{https://en.wikipedia.org/wiki/Binary_search_tree}), only one branch of the tree needs to be searched.  
\end{questions}

\end{document}