\documentclass{exam}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{amsmath}
\usepackage{mathpartir}
\usepackage{ebproof}
\usepackage{flagderiv} 

\let\OldTexttt\texttt

\renewcommand{\texttt}[1]{\OldTexttt{\color{teal}{#1}}}
\definecolor{mGreen}{rgb}{0,0.6,0}
\definecolor{mGray}{rgb}{0.5,0.5,0.5}
\definecolor{mPurple}{rgb}{0.58,0,0.05}
\definecolor{mGreen2}{rgb}{0.05,0.65,0.05}
\definecolor{mGray2}{rgb}{0.55,0.55,0.55}
\definecolor{mPurple2}{rgb}{0.63,0.05,0.05}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}
\definecolor{backgroundColour2}{rgb}{0.95,0.92,0.95}

\lstdefinestyle{C}{
    backgroundcolor=\color{backgroundColour},   
    commentstyle=\color{mGreen},
    keywordstyle=\color{blue},
    numberstyle=\tiny\color{mGray},
    stringstyle=\color{mPurple},    
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    language=C
}

\definecolor{t_comment}{rgb}{0.2,1,0.2}
\definecolor{t_mGray}{rgb}{0.5,0.5,0.5}
\definecolor{t_mPurple}{rgb}{0.58,0,0.05}
\definecolor{t_blue}{rgb}{0.4,0.6,0.8}
\definecolor{t_mGreen2}{rgb}{0.05,0.65,0.05}
\definecolor{t_mGray2}{rgb}{0.75,0.75,0.75}
\definecolor{t_mPurple2}{rgb}{0.63,0.05,0.05}
\definecolor{t_bg}{rgb}{0.15,0.15,0.18}

\lstdefinestyle{terminal}{
    backgroundcolor=\color{t_bg},   
    commentstyle=\color{t_comment},
    keywordstyle=\color{t_blue},
    numberstyle=\tiny\color{t_mGray},
    stringstyle=\color{t_mGray2}, 
    basicstyle=\footnotesize\color{t_mGray2},
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=none,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    language=C
}

\graphicspath{{.}}
\begin{document}

\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
\Large{COMPSCI 3MI3 : Assignment 3} \\
\large{Fall 2021} \\ 
Nicholas Moore}}}
\end{center}

Solutions submitted as a \LaTeX generated pdf file are eligible for 1 bonus point, so long as the source file is included with submission.  
\begin{center}

List of Theorems in Topic 3 \\
\begin{tabular}{| c | c |}
\hline
Theorem & slide no. \\ \hline
Determinacy of Single Step Evaluation & 19 \\ \hline
Every Value is in Normal Form & 29 \\ \hline
If $t$ is in Normal Form, $t$ is a Value & 30 \\ \hline
Uniqueness of Normal Forms & 35 \\ \hline
Termination of Evaluation & 37 \\ \hline
\end{tabular}

\end{center}

\begin{questions}
\question[10] \textbf{Adding Addition}

Our UAE language is pretty bare bones by any objective standard.  Let's fill it out very slightly by adding an addition operator.  \\ 

Propose both syntax and small step semantics for an addition operator, which operates on numeric values.  Please present your syntax in EBNF, and your semantics as a set of one or more inference rules.  The theorems listed above above should still hold, if your proposed term is added to UAE.  

\question[15] \textbf{Determinacy of Single Step Evaluation}

If a language is determinate, then, for any term $t$ and the evaluation relation $\rightarrow$, the single-step evaluation of $t$ is unique.  Another way to say this is: 

\begin{equation}
t \rightarrow t' \land t \rightarrow t'' \implies t' = t''
\end{equation}

In topic 4, we demonstrated this result for the Boolean subset of UAE.  Prove that this result still holds for UAE when we add our semantics for arithmetic expressions.    

\end{questions}
\end{document}