\documentclass[11pt,fleqn]{article}

\setlength {\topmargin} {-.15in}
\setlength {\textheight} {8.6in}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{color}

\renewcommand{\labelenumii}{\theenumii.}

\newcommand{\bsp}{\begin{sloppypar}}
\newcommand{\esp}{\end{sloppypar}}
\newcommand{\mname}[1]{\mbox{\sf #1}}
\newcommand{\tarrow}{\rightarrow}
\newcommand{\pnote}[1]{{\langle \text{#1} \rangle}}
\newcommand{\sB}{\mbox{$\cal B$}}
\newcommand{\sC}{\mbox{$\cal C$}}
\newcommand{\sF}{\mbox{$\cal F$}}
\newcommand{\sP}{\mbox{$\cal P$}}
\newcommand{\sV}{\mbox{$\cal V$}}

\begin{document}

\begin{center}

  {\large \textbf{COMPSCI/SFWRENG 2FA3}}\\[2mm]
  {\large \textbf{Discrete Mathematics with Applications II}}\\[2mm]
  {\large \textbf{Winter 2020}}\\[8mm]
  {\huge \textbf{Extra Credit Assignment 2}}\\[6mm]
  {\large \textbf{Dr.~William M. Farmer}}\\[2mm]
  {\large \textbf{McMaster University}}\\[6mm]
  {\large Revised: January 30, 2020}

\end{center}

\medskip

Extra Credit Assignment 2 consists of one problem.  You must write
your solution to the problem using LaTeX.

\bsp
Please submit Extra Credit Assignment~2 as two files,
\texttt{EC\_Assignment\_2\_\emph{YourMacID}.tex} and
\texttt{EC\_Assignment\_2\_\emph{YourMacID}.pdf}, to the Extra Credit
Assignment~2 folder on Avenue under Assessments/Assignments.
\texttt{\emph{YourMacID}} must be your personal MacID (written without
capitalization).  The \texttt{EC\_Assignment\_2\_\emph{YourMacID}.tex}
file is a copy of the LaTeX source file for this assignment
(\texttt{EC\_Assignment\_2.tex} found on Avenue under
Contents/Assignments) with your solution entered after the problem.
The \texttt{EC\_Assignment\_2\_\emph{YourMacID}.pdf} is the PDF output
produced by executing
\esp

\begin{itemize}

  \item[] \texttt{pdflatex EC\_Assignment\_2\_\emph{YourMacID}}

\end{itemize}

This assignment is due \textbf{Sunday, February 16, 2020 before
  midnight.}  You are allow to submit the assignment multiple times,
but only the last submission will be marked.  \textbf{Late submissions
  and files that are not named exactly as specified above will not be
  accepted!}  It is suggested that you submit your preliminary
\texttt{EC\_Assignment\_2\_\emph{YourMacID}.tex} and
\texttt{EC\_Assignment\_2\_\emph{YourMacID}.pdf} files well before the
deadline so that your mark is not zero if, e.g., your computer fails
at 11:50 PM on February~16.

\textbf{Although you are allowed to receive help from the
  instructional staff and other students, your submission must be your
  own work.  Copying will be treated as academic dishonesty! If any of
  the ideas used in your submission were obtained from other students
  or sources outside of the lectures and tutorials, you must
  acknowledge where or from whom these ideas were obtained.}

\newpage

\subsection*{Background}

A set $S$ is \emph{countably infinite} if there is a bijective
function from $S$ to $\mathbb{N}$.  $S$ is \emph{countable} if it is
finite or countably infinite.  


\subsection*{Extra Credit Problem \textbf{[2 bonus points]}}

Let $\Sigma = (\sB,\sC,\sF,\sP,\tau)$ be a signature of MSFOL.  Assume
that $\sV$ is countably infinite and $\sB$, $\sC$, $\sF$, and $\sP$
are countable.  Show that $F_{\Sigma}$, the set of $\Sigma$-formulas,
is countably infinite.  Hint: Use G\"odel numbering to assign a unique
natural number to each formula in $F_{\Sigma}$.


\bigskip

\noindent
\textcolor{blue}{\textbf{Put your name, MacID, and date here.}}

\bigskip

\noindent
\textcolor{blue}{\textbf{Put your solution here.}}

\end{document}


